A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-01-07 manuscript/manuscript.qmd

For the secondary endpoints of interest (e.g., median survival time or survival probabilities) only the quantitative SMD agreement metric will be applicable.

>>>>

For the secondary endpoints of interest (e.g., median survival time or survival probabilities) only the SMD agreement metric will be applicable.
